%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publicaciones seleccionadas}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\vspace{1mm}

\cvsubsection{Fracturas naturales y reservorios}
\vspace{1.5mm}

\begin{cvparagraph}

\descriptionstyle{%
\textbf{Correa-Luna, C., Yagupsky, D.L., Likerman, J., Barcelona, H.} (2025).
Impact of large-scale structures on fracture network connectivity: Insights into the Vaca Muerta unconventional play, Neuquén basin, Argentina.
\textit{Tectonophysics}, 230640.}

\vspace{1.5mm}

\descriptionstyle{%
\textbf{Correa-Luna, C., Yagupsky, D.L., Likerman, J., Barcelona, H.} (2022).
Natural fracture characterization of the Los Catutos Member (Vaca Muerta Formation) in the southern sector of the Sierra de la Vaca Muerta, Neuquén Basin, Argentina.
\textit{Journal of South American Earth Sciences}, 120, 104081.}

\vspace{1.5mm}

\descriptionstyle{%
\textbf{Correa-Luna, C., Yagupsky, D.L., Likerman, J.} (2019).
Fracture network analysis of Yacoraite Formation in the Tres Cruces sub-basin, northwestern Argentina.
\textit{Journal of South American Earth Sciences}, 102446.}

\vspace{1.5mm}

\descriptionstyle{%
\textbf{Plotek, B., Likerman, J., Cristallini, E.} (2024).
Geomechanical modeling of fault-propagation folds: A comparative analysis of finite-element and the trishear kinematic model.
\textit{Journal of Structural Geology}, 105064.}

\vspace{1.5mm}

\descriptionstyle{%
\textbf{Cilona, A., Aydin, A., Likerman, J., Parker, B., Cherry, J.} (2016).
Structural and statistical characterization of joints and multi-scale faults in an alternating sandstone and shale turbidite sequence.
\textit{Journal of Structural Geology}, 85, 95--114.}

\end{cvparagraph}
